Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-09-09 response.md

We thank the referee for the very thorough analysis and for the detailed suggestions that helped to improve the analysis and the paper overall. In the following, we provide the original comment by the referee, followed by our response.

The major changes in the manuscript have been marked in red boldface. We note that the reorganization of Section 4 (Major Issue I) is not marked. There has also been a mild amount of reordering of tables and figures as a result. We have added a single figure (Figure 11) that shows the fraction of correctable galaxies distributed over the sample, and a short amount of explanatory text in Sections 4.2 and 8.

@@

We have added text to explicitly mark the difference between the two equations in what is now Section 4.2.

-----------------------------------
Minor Comment 4
-----------------------------------

***4) I probably should have mentioned this above, but why are the authors not working with equation (4) as the basis of their regression model?***

Equation 2 was originally left unbounded because the raw data being fit was inherently bounded between vote fractions of 0 and 1. However, the original version of Equation 4 could produce vote fractions greater than 1 for certain combinations of z and f_0 if left in the same form as Equation 2. We have realized that the difference in normalization, while having only a small effect on the fitting of the data, is inconsistent and may be confusing to a reader. Therefore, we have changed Equation 2 to match Equation 4 (see response to Major Comment II, as well as Minor Comment 3). All data in the tables and catalog have been updated to account for these small changes.

@@

Correct, thank you. This typo has been edited in the caption (now Figure 10).

---------------------------------
Minor Comment 6
----------------------------------

***6) How many data points are there in Figure 8? Obviously more than 37, but fewer than 37 x 8.***

The final version of this figure (now Figure 10; changed slightly based on the new form of Equation 4) has 28 unique galaxies, each with multiple images that have been artificially redshifted in between three to eight bins.

@@

----------------------------------
Minor Comment 7
----------------------------------

***7) Section 4.2: "The boundaries [of the convex hull] are then adjusted until the contamination from both groups is minimized." If I look at Figure 9, it would appear that the correctable and lower-limit regions can be perfectly separated (using a tree, for instance). Am I wrong about this?***

The regions in Figure 9 (now Figure 7) can be nearly perfectly separated in f_features-redshift space, but there are a few regions near the edges in which there is overlap between the two populations. This is affected slightly in the figure by the choice of bin size and location. However, our analysis makes the assumption that a true/physical separation should be a smooth function of z-mu-f. Implementing a convex hull in this space created a very small volume near the edge of the inner convex hull that had overlapping positive and negative data points; we optimize the overall accuracy of the hull by adjusting the outer boundaries as described in what is now Section 4.1.

### 2016-09-09 writeup/gz_hubble_data.tex
New figure on correctable fractions and evolving thresholds. Closes #187.

The unshaded regions in Figure~\ref{fig:f_vs_f} define discrete ranges of redshift,
surface brightness, and \ffeatures{} within which a galaxy must lie in order for the
debiased correction to be confidently applied.
While the appropriate correctable regions were defined as discrete bins, the true
correctable region is assumed to be a smooth function of $z$, $\mu$, and
\ffeatures{}. To define this smooth space, we calculate the shape of the convex
hull that encloses the correctable and lower-limit \ferengi{} galaxies in
$z$-$\mu$-\ffeatures{} space. The boundaries are then adjusted until the
contamination from both groups is minimised. The resulting hulls define the
correctable and lower-limit regions for categorising the \hst{} galaxies. The
results of this method and final categorisation of the \hst{} sample are in
Table~\ref{tbl:hubble_debiasable}. Of the galaxies at redshift higher than
$z=0.3$, 17\% can be debiased using the $\zeta$ method, 27\% cannot be debiased
since the relationship between \ffeaturesz{} and \ffeaturesrest{} is not
monotonic, and 56\% cannot be debiased since they either have an unknown
redshift or insufficient numbers of \ferengi{} images in their $z$-$\mu$ bin
to determine a reliable correction term ($\zeta$, described in section ~\ref{ssec:zeta}).

@@

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/zeta_examples_sorted.pdf}
\caption{]Behaviour of the normalised, weighted vote fractions of features
visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the
artificial \ferengi{} images. Galaxies in this plot were randomly selected from
a distribution with $e=0$ and at least three detectable images in redshift bins
of $z\ge0.3$, and are sorted by \ffeaturesrest. Measured vote fractions (blue
solid line) are fit with an exponential function (red dashed line;
Equation~\ref{eqn:fzeta}); the best-fit parameter for $\zeta$ is given above
each plot.}
% Error bars are binomial for each f, symmetrised, then added in quadrature.
\label{fig:zeta_examples}
\end{figure*}

@@

@@

The data in the GZH catalogues have been extensively reduced and tested. A
dominant effect is the known bias against identifying disky and asymmetric
sub-structures at either low resolution or surface brightness. This can be the
result either of genuinely small or dim galaxies, or a perceived effect from
observing galaxies at further distances (higher redshift). To calibrate this
\emph{without} potentially overcorrecting for the genuine morphological
evolution of galaxies over cosmic time, the GZH project uses SDSS images of
low-redshift galaxies, processes them to appear as if they were at higher
redshift, and classifies them through the GZH interface in an identical
fashion. The resulting change in \ffeatures{} as a function of $z$ and $\mu$ is
applied as a multiplicative correction to the top-level vote fractions for
$\sim50\%$ of the GZH galaxies.

>>>>

The unshaded regions in Figure~\ref{fig:f_vs_f} define discrete ranges of redshift,
surface brightness, and \ffeatures{} within which a galaxy must lie in order for the
debiased correction to be confidently applied.
While the appropriate correctable regions were defined as discrete bins, the true
correctable region is assumed to be a smooth function of $z$, $\mu$, and
\ffeatures{}. To define this smooth space, we calculate the shape of the convex
hull that encloses the correctable and lower-limit \ferengi{} galaxies in
$z$-$\mu$-\ffeatures{} space. The boundaries are then adjusted until the
contamination from both groups is minimised. The resulting hulls define the
correctable and lower-limit regions for categorising the \hst{} galaxies. The
results of this method and final categorisation of the \hst{} sample are in
Table~\ref{tbl:hubble_debiasable}. Of the galaxies at redshift higher than
$z=0.3$, 17\% can be debiased using the $\zeta$ method, 27\% cannot be debiased
since the relationship between \ffeaturesz{} and \ffeaturesrest{} is not
monotonic, and 56\% cannot be debiased since they either have an unknown
redshift or insufficient numbers of \ferengi{} images in their $z$-$\mu$ bin
to determine a reliable correction term ($\zeta$, described in Section~\ref{ssec:zeta}).

@@

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/zeta_examples_sorted.pdf}
\caption{Behaviour of the normalised, weighted vote fractions of features
visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the
artificial \ferengi{} images. Galaxies in this plot were randomly selected from
a distribution with $e=0$ and at least three detectable images in redshift bins
of $z\ge0.3$, and are sorted by \ffeaturesrest. Measured vote fractions (blue
solid line) are fit with an exponential function (red dashed line;
Equation~\ref{eqn:fzeta}); the best-fit parameter for $\zeta$ is given above
each plot.}
% Error bars are binomial for each f, symmetrised, then added in quadrature.
\label{fig:zeta_examples}
\end{figure*}

@@

\begin{figure}
\center
\includegraphics[width=0.5\textwidth]{figures/correctable_fraction.pdf}
\caption{\changes{Histogram showing the fraction of galaxies that have a finite correction
for the debiased vote fractions \ffeaturesdebiased{} as a function of \ffeatures{}
and redshift. The parameter space for corrections is limited to $0.3 \leq z \leq 1.0$
due to the sampling of the parent SDSS galaxies and detectability in the \ferengi{} images.}
}
\label{fig:correctable_fraction}
\end{figure}

\changes{Figure~\ref{fig:correctable_fraction} shows the
distribution of the fraction of galaxies that are ultimately correctable as a function
of \ffeatures{} and redshift. The distributions for individual samples (AEGIS, COSMOS,
GEMS, GOODS) are individually very similar. We emphasize that a correction is more likely to be derived
and applied for galaxies at higher redshift and with higher weighted values of \ffeatures.
This has important consequences for selection of physically meaningful samples from GZH
(see Section~\ref{sec:cookbook}), meaning that comparative studies of galaxies
should use a threshold on the likelihood of features that evolves as a function of redshift.}

@@

The data in the GZH catalogues have been extensively reduced and tested. A
dominant effect is the known bias against identifying disky and asymmetric
sub-structures at either low resolution or surface brightness. This can be the
result either of genuinely small or dim galaxies, or a perceived effect from
observing galaxies at further distances (higher redshift). To calibrate this
\emph{without} potentially overcorrecting for the genuine morphological
evolution of galaxies over cosmic time, the GZH project uses SDSS images of
low-redshift galaxies, processes them to appear as if they were at higher
redshift, and classifies them through the GZH interface in an identical
fashion. The resulting change in \ffeatures{} as a function of $z$ and $\mu$ is
applied as a multiplicative correction to the top-level vote fractions for
$\sim50\%$ of the GZH galaxies. \changes{However, any population studies using
GZH morphological data must use a combination of debiased vote fractions
and upper limits from the ``uncorrectable'' galaxies, due to the evolving nature
of the thresholds as a function of redshift.}
